Iconic representations of molluscs through the ages

### 2012-10-18 large_number_squeezing_with_atoms.tex
Add some bullet points to intro as a test
Address adjustment as commit test
Trivial change to try using github for the first time.

\address{$^1$Department of Quantum Science, The Australian National University, Canberra ACT 0200, Australia}
\address{$^2$Research School of Physics and Engineering, The Australian National University, Canberra ACT 0200, Australia}
\ead{mattias.johnsson@anu.edu.au}

@@

\section{Introduction}
Wibble.

>>>>

\address{$^1$Department of Quantum Science, Research School of Physics and Engineering, The Australian National University, Canberra ACT 0200, Australia}
\address{$^2$Plasma Research Laboratory, Research School of Physics and Engineering, The Australian National University, Canberra ACT 0200, Australia}
\ead{mattias.johnsson@anu.edu.au}

@@

\section{Introduction}
\begin{itemize}
  \item General non-classical state generation with atoms
  \item Talk about number squeezing with atoms
  \item Link to interferometry
  \item Motivate why large number squeezing
  \item Point out no one has done it before, only low number squeeze
  \item Lay out what sections we have and what we've done
\end{itemize}
